### 2016-04-04 Projects/DelCo_2012/Report/DelCo_2012.tex
update script and cafs report

\section{Fire Suppression}
\label{sec:Fire_Suppression}
There were 14 suppression tests conducted in the single story purpose-built concrete structure. Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}). The fires were intended to replicate room and contents fires typically seen within residential structures. Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle). Each nozzle flowed 15~s of water or compressed air foam depending on the test. The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack). The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack). Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
\centering
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream				& Flow Rate			& Fuel           & Ventilation     \\
\midrule
 1 & CAF~1    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
 3 & CAF~2 	  &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 4 & Water~2  &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 6 & CAF~3    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 8 & CAF~4    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
12 & CAF~5    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
14 & CAF~6    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

@@

The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83\~{}m (6\~{}ft) below the ceiling.  During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling. It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.  Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.  There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.

@@

In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.  Typically the volumetric flow rate of water was 120 gpm.  The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .  The average time of flow was 15 s, therefore a total of X kg of water was introduced into each gas cooling experiment.  When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.  Also calc the mass of air in the stream.

@@

>>>>

\section{Fire Suppression}
\label{sec:Fire_Suppression}

\subsubsection*{Single Story Structure}
\label{sec:fire_supp_single}

There were 14 suppression tests conducted in the single story purpose-built concrete structure. Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}). The fires were intended to replicate room and contents fires typically seen within residential structures. Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle). Each nozzle flowed 15~s of water or compressed air foam depending on the test. The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack). The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack). Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
\centering
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel           & Ventilation     \\
\midrule
 1 & CAF~1    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
 3 & CAF~2 	  &  7/8'' Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 4 & Water~2  &  7/8'' Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 6 & CAF~3    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 8 & CAF~4    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
12 & CAF~5    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
14 & CAF~6    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\subsubsection*{Two Story Structure}
\label{sec:fire_supp_two}

\begin{table}[!ht]
\centering
\footnotesize
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
\midrule
 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41c & CAF~9b    &  7/8'' Slub      	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results}\label{tab:Test_Results_2}
\begin{tabular}{lccc}
\toprule[1.5pt]
                     & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	             & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 1~m (3~ft) Above Floor \\
\midrule
CAF~7 Stairell       & 579~$^{\circ}$C - 258~$^{\circ}$C   & 487~$^{\circ}$C - 193~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7 Stairwell    & 514~$^{\circ}$C - 260~$^{\circ}$C   & 454~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a Stairwell     & 474~$^{\circ}$C - 283~$^{\circ}$C   & 422~$^{\circ}$C - 249~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b Stairwell     & 452~$^{\circ}$C - 238~$^{\circ}$C   & 388~$^{\circ}$C - 189~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Class A~1 Stairwell  & 441~$^{\circ}$C - 304~$^{\circ}$C   & 258~$^{\circ}$C - 234~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a Stairwell     & 468~$^{\circ}$C - 270~$^{\circ}$C   & 418~$^{\circ}$C - 234~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b Stairwell     & 508~$^{\circ}$C - 336~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\section{Gas Cooling}
\label{sec:Gas_Cooling_discuss}

@@

The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling. During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling. It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks. Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer. There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.

In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream. Typically the volumetric flow rate of water was 120 gpm. The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .  The average time of flow was 15~s, therefore a total of X kg of water was introduced into each gas cooling experiment. When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.  Also calc the mass of air in the stream.

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression_discussion}
